### 2014-02-23 paper/retrofit.tex
Start adding typing.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\begin{figure}
\begin{code}
tv   ::= \tx.te | true | false | ta
te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te
tE   ::= tHole | tE te | tv tE | if tE then te else te
       | ref tE | !tE | tE := te | tv := tE

@@

@@

>>>>

\begin{figure}
\begin{code}
tv   ::= \tx.te | true | false | ta
tt   ::= bool | tt -> tt | ref tt
te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te
tE   ::= tHole | tE te | tv tE | if tE then te else te
       | ref tE | !tE | tE := te | tv := tE

@@

Typing judgment: $|tyrule tG tS te tt|$

@@

\begin{figure}
\begin{mathpar}

\end{mathpar}

\caption{Typing rules for ML-like language}
\label{fig:ml-typing}
\end{figure}
